---
title: "History of Calculated Statistics"
author: "Liam Marley"
date: "8 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting Functions
```{r}
# t-test
p_from_t <- function(t, df) {
  round(2*pt(t, df, lower.tail = F), 3)
}

# F-test
p_from_F <- function(f, df1, df2) {
  round(pf(f, df1, df2, lower.tail = F), 3)
}

# Pearson's correlation
p_from_r <- function(r, df) {
  rt <-  sqrt(df) * r/sqrt(1 - r^2)
  pval <- round(2 * min(pt(rt, df), pt(rt, df, lower.tail = FALSE)), 3)
  return(pval)
}

# Standard deviation of the mean

# If the standard error is provided
# where se = the standard error, and n = group size

SD_from_SE <- function(se, n) {
  n <- sqrt(n)
  sd <- round((se/n), 2)
  return(sd)
}
```

## History

For each entry give the publication ID as the title, then provide the: authors, year, and page of the statistic. Followed by the type of calculation as a subtitle. 

### 177

Chu et al. (2015)
pp. 178

#### Standard Deviation of the Mean

##### Beck's Depression Inventory

```{r}
# Control Group

SD_from_SE(.64, 74)

# Suicide Attempt

SD_from_SE(3.04, 17)
```

##### Use of Each Perspective

For the delayed task recall memories.

```{r}
# Field perspective - Control group
SD_from_SE(.14, 74)

# Observer perspective - Control group
SD_from_SE(.12, 74)

# Field perspective - Suicide attempt
SD_from_SE(.35, 17)

# Observer perspective - Suicide attempt
SD_from_SE(.27, 17)
```

Realised the above is redundant as it's only comparing the extent each perspective was used rather than frequency per se. Pending discussion now and another possible change to the scheme may be needed. At any rate, it provides an exemplar at least. 