---
title: "History of Calculated Statistics"
author: "Liam Marley"
date: "8 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting Functions

Exact p-value from a t-test
```{r}
p_from_t <- function(t, df) {
  pval <- 2*pt(-abs(t), df, lower.tail = TRUE)
  pval <- round((pval), 4)
  return(pval)
}
```

Exact p-value from a F-test
```{r}
# F-test
p_from_F <- function(f, df1, df2) {
  round(pf(f, df1, df2, lower.tail = F), 3)
}
```

Exact p-value from Pearson's correlation
```{r}
p_from_r <- function(r, df) {
  rt <-  sqrt(df) * r/sqrt(1 - r^2)
  pval <- round( 2 * min( pt(rt, df), pt(rt, df, lower.tail = FALSE) ), 3 )
  return(pval)
}
```

Standard Deviation of the mean, from the Standard Error
```{r}
# If the standard error is provided
# where se = the standard error, and n = group size

SD_from_SE <- function(se, n) {
  sd <- round((se * sqrt(n - 1)), 2)
  return(sd)
}
```

Independent samples t-test
```{r}
# m1, m2: the sample means
# s1, s2: the sample standard deviations
# n1, n2: the group sizes
# m0: the null value for the difference in means to be tested for. Default is 0. 
# equal.variance: whether or not to assume equal variance. Default is FALSE. 
t_test2 <- function(m1, m2, sd1, sd2, n1, n2, m0=0, equal.variance = FALSE)
{
    if(equal.variance == FALSE) 
    {
        se <- sqrt( (sd1^2/n1) + (sd2^2/n2) )
        # welch-satterthwaite df
        df <- ( (sd1^2/n1 + sd2^2/n2)^2 )/( (sd1^2/n1)^2/(n1-1) + (sd2^2/n2)^2/(n2-1) )
    } else
    {
        # pooled standard deviation, scaled by the sample sizes
        se <- sqrt( (1/n1 + 1/n2) * ((n1-1)*sd1^2 + (n2-1)*sd2^2)/(n1+n2-2) ) 
        df <- n1+n2-2
    }      
    t <- (m1-m2-m0)/se 
    dat <- c(m1-m2, se, t, df, 2*pt(-abs(t), df))    
    names(dat) <- c("Difference of means", "Std Error", "t", "df", "p-value")
    return(dat) 
}
```

## History

For each entry give the publication ID as the title, then provide the: authors, year, and page of the statistic/info. Followed by the type of calculation as a subtitle. 

### 177

Chu et al. (2015)
pp. 178

#### Standard Deviation of the Mean

##### Beck's Depression Inventory

```{r}
# Control Group

SD_from_SE(.64, 74)

# Suicide Attempt

SD_from_SE(3.04, 17)
```

##### Use of Each Perspective

For the delayed task recall memories.

```{r}
# Field perspective - Control group
SD_from_SE(.14, 74)

# Observer perspective - Control group
SD_from_SE(.12, 74)

# Field perspective - Suicide attempt
SD_from_SE(.35, 17)

# Observer perspective - Suicide attempt
SD_from_SE(.27, 17)
```

Realised the above is redundant as it's only comparing the extent each perspective was used rather than frequency per se. Pending discussion now and another possible change to the scheme may be needed. At any rate, it provides an exemplar at least. 

### 379

Vella and Moulds (2014)
pp. 259

#### Exact p-value

Recency, pre-scores, between-subjects
```{r}
p_from_t(2.00, 72)
```

Emotional Intensity
```{r}
p_from_t(.62, 72)
```


Vividness, pre-scores, between-subjects
```{r}
p_from_t(.84, 72)
```

#### Independent t-tests

Recency, between-subjects, pre-score
pp.260
This won't change across the shift so it has been coded
```{r}
t_test2(7.36, 10.53, 6.96, 6.47, 42, 32)
```

Vividness, between-subjects, post-score
pp.260
```{r}
t_test2(69.69, 66.31, 25.05, 21.27, 32, 42)
```

Happiness/Positive Emotion, between-subjects, post-scores
pp.260
```{r}
t_test2(82.19, 70.95, 20.32, 19.07, 32, 42)
```

Vividness, between-subjects, pre-score (naturalistic)
pp.260
```{r}
t_test2(80.00, 76.72, 12.83, 20.54, 42, 32)
```

Happiness, between-subjects, pre-score (naturalistic)
pp.260
```{r}
t_test2(81.76, 86.38, 13.07, 12.32, 42, 32)
```

Recency, between-subjects, pre-score (naturalistic)
pp.260
```{r}
t_test2(7.36, 10.53, 6.96, 6.47, 42, 32)
```


### 255

Marcotti and St Jacques (2018)


#### Exact p-value

Vividness
pp. 334
```{r}
p_from_t(2.73, 19)
```

### 28

McIssac and Eich (2002)

#### Exact p-values

Richness in detail/Vividness, between-subjects
pp. 147
```{r}
p_from_t(3.27, 50)
```

Emotionality/Emotional Intensity, between-subjects
pp. 147
```{r}
p_from_t(4.12, 50)
```

They haven't provided the standard deviations or standard errors for these means.

### 94

Sutin and Robins (2010)

### t-tests

Vividness, spontaneous/naturalistic, between-subjects
pp. 632
```{r}
t_test2(4.22, 3.72, .69, .76, 335, 115, equal.variance = F)
```

Emotional Intensity, spontaneous/naturalistic, between-subjects
pp. 632
```{r}
t_test2(4.04, 3.63, .82, .85, 335, 115, equal.variance = F)
```

Vividness, deliberate, between-subjects
pp.632
```{r}
t_test2(4.02, 3.96, .68, .78, 128, 128, equal.variance = F)
```

Emotional Intensity, deliberate, between-subjects
pp. 632
```{r}
t_test2(3.76, 3.66, .84, .84, 128, 128, equal.variance = F)
```

Sharing/Rehearsal, deliberate, between-subjects
pp.632
```{r}
t_test2(2.8, 2.95, 1.07, 1.02, 128, 128)
```
I've treated sharing as an analgoue to rehearsal because it concerns the frequency of discussing the memory with others.

#### Exact p-values

Perspective use, deliberate, between-subjects
They've used a single scale for the use of first-person perspective
pp. 632
```{r}
p_from_F(5.40, df1 = 1, df2 = 254)
```

### 50
Bernsten & Rubin (2006)

#### t-tests

Visual Imagery/Vividness, deliberate, between-subjects
pp.1205
```{r}
t_test2(5.19, 5.31, 0.68, 0.77, 42, 40, equal.variance = F)
```

Emotional Intensity, deliberate, between-subjects
pp. 1205
```{r}
t_test2(4.75, 4.79, .93, 1.09, 42, 40, equal.variance = F)
```

Reliving/Re-experiencing, deliberate, between-subjects
pp. 1205
```{r}
t_test2(4.51, 4.65, 0.87, 0.94, 42, 40, equal.variance = F)
```

Rehearsal, deliberate, between-subjects
pp. 1205
```{r}
t_test2(3.5, 3.73, .89, .74, 42, 40)
```


Retention Interval/Age of memory, deliberate, between-subjects
pp. 1205
```{r}
t_test2(5.14, 5.87, 3.07, 3.15, 42, 40, equal.variance = F)
```

### 91
Robinaugh and McNally (2010)

#### t-tests

Emotional Intensity
pp.649
```{r}
t_test2(4.9, 4.4, 1.53, 1.83, 24, 93, equal.variance = F)
```

### 1
Nigro and Neisser (1983)

#### Exact p-values

Vividness, study 3
```{r}
p_from_t(2.13, 31)
```

Recency/Age of Memory, Study 3
```{r}
p_from_t(2.97, 31)
```

### 136
Sekiguchi and Nonaka (2014)

#### Independent t-tests

Session 2 was chosen because it allows for a comparison between first and third person perspective with known group sizes, and at the participant level of analysis. 

Choice between the field vs observer event was arbitary and done to avoid the issues of assuming the covariance matrix to be able to aggregate the SDs (they are paired data). Mainly due to how many assumptions about covariances that will have to be made to do the multivariate analysis. 

Vividness, between-subject (chnage vs no change) at session 2
pp.377
```{r}
t_test2(3.1, 3.5, 0.7, 0.5, 24, 24)
```


Reliving/Re-Experiencing, between-subjects (change vs no change) at session 2
pp. 377
```{r}
t_test2(2.7, 2.9, 0.6, 0.6, 24, 24)
```

### 15
West and & Bauer (1999)

#### Frequencies

Only the percentage of memories is provided, for the effect size I'd prefer to have the calculations all done together and by metafor for consistency and reproducibility.

Each participant contributed 8 memories in total, 4 for the remote memories and 4 for the recent memories. As per the coding scheme only the most recent memories are sourced. 

Study 1
pp. 268
```{r}
# Sample size was 48 
# proportion of first person memories was .82
(48*4)*0.82

# proportion of third person was .18
(48*4)*.18

# Total number of memories
48*4
```
Because decimal memories are not possible I'm rounding to the nearest whole for each frequency calculation. Which added together do return the correct total no. of memories. 

Study 2
pp. 272
Surprisingly, these values are identical to study 1
```{r}
# Sample size was 15
# Proportion of first person memories was .
(15*4)*.82
# Proportion of third person memories was
(15*4)*.18
# Total number of memories
15*4
```

## 102
Wisco and Nolen-Hoeksema (2011)

Note, their use of 're-experiencing' is in relation to re-experiencing the negative emotion of the event, not the sense of reliving the memory. 

Each group is an independent sample: 
* Control & first person, n = 28
* Control & third person, n = 30
* Dysphoric & first person, n = 25
* Dysphoric & third person, n = 27

### Standard Deviations - Control Group

Emotional intensity, control group, first-person
pp. 409
```{r}
SD_from_SE(0.27, 28)
```

Emotional intensity, control group, third-person
pp. 409
```{r}
SD_from_SE(0.26, 30)
```

Negative Emotion, control group, first-person
pp.409
```{r}
SD_from_SE(0.28, 28)
```

Negative Emotion, control group, third-person
pp.409
```{r}
SD_from_SE(0.27, 30)
```

### Independent t-tests - Control Group

Emotional Intensity, deliberate, control group
pp.409
```{r}
t_test2(3.96, 3.44, 1.4, 1.4, 28, 30)
```

Negative Emotion, deliberate, control group
pp.409
```{r}
t_test2(4.28, 4.04, 1.45, 1.45, 28, 30)
```

### Standard Deviations - Dysphoric Group

Emotional Intensity, dysphoric, first-person
pp.409
```{r}
SD_from_SE(0.31, 25)
```

Emotional Intensity, dysphoric, third-person
pp.409
```{r}
SD_from_SE(0.27, 27)
```

Negative Emotion, dysphoric, first-person
pp.409
```{r}
SD_from_SE(0.31, 25)
```

Negative Emotion, dysphoric, third-person
pp.409
```{r}
SD_from_SE(0.28, 28)
```

### Independent t-tests - Dysphoric Group

Emotional Intensity, deliberate, dysphoric
pp.409
```{r}
t_test2(5.3, 4.70, 1.52, 1.38, 25, 27)
```

Negative Emotion, deliberate, dysphoric
pp. 409
```{r}
t_test2(5.48, 5.07, 1.52, 1.45, 25, 28)
```

## 63
Williams and Moulds (2008)

### Independent t-tests - Post-Shift

Vividness, post-shift scores, dysphoric
pp. 747
```{r}
t_test2(69.27, 60.38, 23.71, 23.65, 55, 78)
```

Reliving/Re-experiencing, post-shift scores, dsyphoric
pp. 747
```{r}
options(scipen = 99)
t_test2(54.54, 41.02, 27.54, 28.90, 55, 78)
```

Distress/Negative Emotion, post-shift scores, dysphoric
pp. 747
```{r}
t_test2(60.36, 48.71, 23.72, 24.98, 55, 78)
```


### Independent t-tests - Pre-Shift (Naturalistic)

Vividness, pre-shift, dysphoric
pp. 746
```{r}
t_test2(68.39, 72.00, 22.68, 21.20, 78, 55)
```

Reliving/Re-experiencing, pre-shift, dysphoric
pp. 746
```{r}
t_test2(46.98, 52.72, 25.74, 25.85, 78, 55)
```

Distress/Negative Emotion, pre-shift, dysphoric
pp. 746
```{r}
t_test2(65.83, 68.28, 18.95, 19.12, 78, 55)
```

## 383
Wang et al. (2017)

### Frequencies

15 schizophrenic ps, 9 memories, proportion that are 1st person 
pp. 226
```{r}
# number of 1st person memories
(15*9)*.8969
# number of 3rd person memories
(15*9) - ((15*9)*.8969)
# total number of memories
(15*9)
```
Schizophrenia ps n of 1st person = 121
Schizophrenic ps n of 3rd person = 14

15 control ps, 9 memories, proportion that're 1st person
```{r}
# number of 1st person memories
(15*9)*.9326
# number of 3rd person memories
(15*9) - ((15*9)*.9326)
# total number of memories
(15*9)
```
Control ps n of 1st person = 126
Control ps n of 3rd person = 9

## 44
Sutin (2006)

Uses the MEQ 

### Independent t-tests
All information sourced from pp.83

Vividness, spontaneous
```{r}
t_test2(4.2, 3.9, .7, .7, 491, 159)
```

Emotional Intensity, spontaneous
```{r}
t_test2(4.0, 3.7, .8, .9, 491, 159)
```

Visual Perspective, spontaneous single scale (higher values indicate greater use of 1st person)
```{r}
t_test2(4.1, 2.8, .7, 1, 491, 159)
```

Sensory Detail/Re-experiencing, spontaneous
```{r}
t_test2(3.6, 3.3, .6, .7, 491, 159)
```

Sharing/Rehearsal, spontaneous
```{r}
t_test2(2.9, 2.7, 1.1, 1.1, 491, 159)
```

